The SMT Competition 2015--2018

### 2019-08-22 2018/report/Reviews_67398_Revised_Response.txt

>  - "DT" looks not to be introduced

WONTFIX ("DT" for algebraic datatypes is introduced in Section 3)

>  - the concept of "benchmarks families" is used at the beginning of pg. 7 but it has not been introduced

DONE (reference to benchmark families removed on page 7; they are now
discussed in Section 7)

@@

>  - [38] contains the only acronym for journal name

DONE

> ============================================
>
> *** Review 2 ***
>
> ummary: This is a much improved revision of this paper. I'm very happy to see
> the additional sections and paragraphs, especially Sec 8! I think this paper is
> ready for publication, modulo a few minor (essentially typesetting) issues (see
> below).
>
> Details:
>
> 4.1 Scoring: A good addition. I think it would be great if the changes to the
> scoring system over the years would be analyzed, to see whether they did indeed
> have the intended effect. This has been started in 8.6, but a more
> comprehensive analysis would be great (possibly as a separate submission here
> or elsewhere).

WONTFIX (we have carried out some analysis to answer this question;
there is certainly ample opportunity for further analysis, but the
present paper already covers a lot of material and we cannot expand
its scope forevermore)

### 2019-08-22 2018/report/SMT-COMP.tex
Minor

For the \emph{\apptrack}, we determine the VBS as the best performance
in terms of number of correct \texttt{check-sat} answers within the time limit
of 2400s (the time limit of the \apptrack in the competitions
2015--2018).
The total number of eligible \texttt{check-sat} queries (i.e., all queries with
status sat or unsat up to the first query with status unknown) on
common benchmarks from 2015--2018 is \num{30370517}.
Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
benchmarks as a bar plot.
In 2015, already 99.95\% of the eligible queries were answered correctly,
which naturally does not leave a lot of room for improvement.
In 2016, performance decreased by \num{185625} correct answers (0.61\%),
which can be entirely attributed to a performance regression
of Z3 on 2 benchmarks in the QF\_NIA division.
%(on which in 2016, CVC4 then
%performed best, and from 2017 onwards even as well as Z3 in 2015).

>>>>

For the \emph{\apptrack}, we determine the VBS as the best performance
in terms of number of correct \texttt{check-sat} answers within the time limit
of 2400s (the time limit of the \apptrack in the competitions
2015--2018).
The total number of eligible \texttt{check-sat} queries (i.e., all queries with
status sat or unsat up to the first query with status unknown) on
common benchmarks from 2015--2018 is \num{30370517}.
Figure~\ref{fig:progress-all-app} visualizes VBS performance on these
benchmarks as a bar plot.
In 2015, already 99.95\% of the eligible queries were answered correctly,
which naturally does not leave a lot of room for improvement.
In 2016, performance decreased by \num{185625} correct answers (0.61\%),
which can be entirely attributed to a performance regression
of Z3 on two benchmarks in the QF\_NIA division.
